\begin{thebibliography}{9}\addcontentsline{toc}{chapter}{Bibliographie}

\bibitem{S}
  Douglas R. Mauro, Kevin J, 2005:
  \emph{Essential SNMP, Second Edition},
  O'Reilly Media, 462 p,
  \url{http://shop.oreilly.com/product/9780596008406.do}
  
\bibitem{SP}
   NGUYEN Manh Tuong.
  \emph{Les protocoles pour la gestion des réseaux Informatiques }.
  2005.
  \url{http://www2.ifi.auf.org/rapports/tpe-promo10/tipe-nguyen_manh_tuong.pdf}
  
\bibitem{AR}
   Yves Bertsch, Frederic Stmarcel.
  \emph{Administration Réseau-système SNMPv1, SNMPv2, SNMPv3 et HTTP }.
  2001.
  \url{http://2001.jres.org/actes/snmpvhttp.pdf}
  
\bibitem{SW}
   Simple Web (Aiko Pras, Ramin Sadre), Design and Analysis of Communications Systems (DACS) group, University of Twente, The Netherlands, 
  \emph{Internet Management Tutorials }.
  2012.
  \url{http://www.simpleweb.org/wiki/Internet_Management_Tutorials}

\bibitem{AT1}
Pandey, Choi, Lee and Hong.
\emph{IP Network Topology Discovery Using SNMP}. 
International Conference on Information Networking (ICOIN'09). 23 33-37 2009
  \url{http://dpnm.postech.ac.kr/papers/ICOIN/09/TopologyDiscovery_November_18.pdf}

\bibitem{AT2}
Yang Xiao.
\emph{Physical Path Tracing for IP Traffic using SNMP}. 
BBC Research White Paper WHP 188 2010

\bibitem{AT3}
Pandey, Choi, Won and Hong.
\emph{SNMP-based enterprise IP network topology discovery}. 
 International Journal of Network Management 21 (3) 169-184. 2011
 
\bibitem{AT4}
Musa Balta, Ibrahim Özçelik
\emph{The Discovery of Enterprise Network Topology Created in a Virtual
Environment with SNMPv3}. 
The Online Journal of Science and Technology (TOJSAT) Volume 2, Issue 2, 64-70, April 2012.


\bibitem{DIT}
  R. Siamwalla, R. Sharma, S. Keshav
  \emph{Discovering Internet Topologym}.
   Cornell Network Research Group, Department of Computer Science, Cornell University, Ithaca, 1988.

\bibitem{PT}  
Bierman and Jones 
\emph{Physical topology MIB}.
IETF web page, 2000
 \url{http://www.ietf.org/rfc/rfc2922.txt} 
 

\bibitem{Py}
  Mark Lutz.
  \emph{Learning Python, Fourth Edition},
  O'Reilly Media, 1214 p, 2009.
  
\bibitem{Py1}
  Mark Lutz.
  \emph{Programming.Python, Fourth Edition},
  O'Reilly Media, 1628 p, 2010.
  %\url{http://shop.oreilly.com/product/9780596008406.do}

 
\end{thebibliography}